### 2018-05-07 Paper/examples.tex
..
borehole, first pass ...

\noindent The radius of influence, $r$ is fixed at 3698.30 m whereas all other parameters
in the RHS of Eq.~\ref{eq:bore} are considered as uncertain. Table~\ref{tab:bore} provides
marginal distributions of the uncertain parameters.

@@

\caption{Description and marginal distributions of uncertain parameters in the borehole function
given by Eq.~\ref{eq:bore}.}
\label{tab:bore}
\end{table}

As mentioned earlier in this section, cheap function evaluations of the discharge using 
Eq.~\ref{eq:bore} enable us to compute converged estimates of $\mathcal{T}(\theta_i)$. Plotted in
Figure~\ref{fig:sense_bore} are estimates of these indices corresponding to the uncertain
parameters in the borehole function using 10$^6$ pseudo-random
samples\footnote{Although $\mathcal{T}(\theta_i)$ 
might converge with much fewer samples depending upon the model, we consider a large number that
typically ensures a converged estimate for the purpose of illustration.} in the input parameter domain. 
These estimates are used to verify fidelity of
parameter screening based on the methodology presented in Section~\ref{sec:method}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.65\textwidth]{./Figures/sense_borehole}
\caption{Sobol' total effect sensitivity index for uncertain parameters in the borehole
function (Eq.~\ref{eq:bore}).}
\label{fig:sense_bore}
\end{center}
\end{figure}

In Figure~\ref{fig:screen_bore}, we plot estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$)
for a wide range of the number of samples used for approximating $\mu_i$ using Eq.~\ref{eq:mu}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.65\textwidth]{./Figures/ub_conv_borehole}
\caption{Estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$) is plotted 
against number of samples considered for evaluating $\mu_i$. Corresponding estimates
for the converged Sobol' total effect index ($\mathcal{T}(\theta_i)$) in each case is also included in the
legend.}
\label{fig:screen_bore}
\end{center}
\end{figure}

\noindent Estimates for $\hat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$
even when small number of samples (5 -- 10) are used. 
Consequently, the relative importance of uncertain 
parameters in the borehole function is found to be consistent with predictions based on the Sobol' index. 
In the considered intervals for the uncertain parameters, it is clear that the discharge is insensitive to
$T_u$ and $T_l$. Moreover, the sensitivity towards $K_w$ is also small. We exploit this result to reduce
the dimensionality of the problem by 
discounting the uncertainties in $T_u$, $T_l$, and $K_w$, while using nominal values for these
parameters instead.

Our goal as discussed is to gain computational advantage by constructing surrogates in a 
reduced input parameter space. To this end, we construct PCE's in 5D and 4D spaces by
fixing $\{T_u,T_l\}$ in the former and additionally fixing $K_w$ in the latter at their respective
mean values. In Figure~\ref{fig:conv_bore}, we compare convergence of PCE's constructed
in the full space (7D) with those constructed in the two reduced spaces (4D and 5D) using
$\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}).

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.65\textwidth]{./Figures/err_samples_borehole}
\caption{A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions.}
\label{fig:conv_bore}
\end{center}
\end{figure}

\noindent As expected, it is observed that the PCE
constructed in the 4D space converges at a much faster rate. For instance, if a PCE with
$\mathcal{O}(10^{-4})$ accuracy is sought, we need function evaluations at only about
50 sample points in the 4D parameter space whereas the number of samples needed in the full 
7D space seems much higher.

As discussed earlier in this section, the reduced order PCE's are verified for predictive accuracy in 
a least-squares sense and a probabilistic sense. Estimates for $\epsilon_{\mbox{\tiny{L-2}}}$
based on 50 samples and corresponding function evaluations in the original 7D parameter space
were found to be 0.0551 and 0.0112 for the 4D and 5D PCE's respectively. In other words, the 4D
PCE is accurate within 5.52$\%$ and the 5D PCE is accurate within 1.12$\%$ of predictions based on
the borehole function. It is interesting to note that although the order of convergence in the case of a 5D
PCE is lower (Figure~\ref{fig:conv_bore}), its predictive accuracy is higher than the 4D PCE. A possible
explanation for this observation is that above a certain order of convergence, the uncertainty in $k_w$ 
contributes much more towards predictive accuracy of the reduced order PCE. It is therefore critical
to account for the order of PCE convergence as well as its predictive accuracy for a given application,
as highlighted earlier in section~\ref{sec:method}.

Figure~\ref{fig:pdfcomp_bore} illustrates a comparison of the PDF's of the discharge, $\mathcal{Q}$
obtained by propagating 10$^6$ Monte-Carlo (MC) samples through the 7D PCE in the
original input parameter domain as well as the reduced order PCE's constructed in 4 and 5 dimensions.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.65\textwidth]{./Figures/pdf_comp_borehole}
\caption{A comparison of PDF's of the discharge, $\mathcal{Q}$ as obtained
by propagating
parametric uncertainties through the 4D, 5D, and 7D PCE's.These PDF's 
were obtained using 10$^{6}$ MC samples in the input parameter domain.} 
\label{fig:pdfcomp_bore}
\end{center}
\end{figure}

\noindent It is evident from this plot, that the PDF's agree quite favorably with each other. Consequently, it can
be said that the reduced order PCE is verified in a probabilistic sense. In other words, the mode as
well as the uncertainty in the observable is reliably captured and predicted by the reduced order PCE.

>>>>

\noindent The radius of influence, $r$ is fixed at 3698.30 m whereas all other parameters
in the right hand side of~\eqref{eq:bore} are considered 
as uncertain. Thus, $\mathcal{Q} = \mathcal{Q}(\vec{\theta})$ with 
\[
   \vec{\theta} = (r_w, L, T_u, H_u, T_l, H_l, K_w)^T.
\] 
Table~\ref{tab:bore} provides distributions of the uncertain inputparameters.

@@

\caption{Description and distributions of uncertain parameters in the borehole function
given by~\eqref{eq:bore}.}
\label{tab:bore}
\end{table}

Cheap function evaluations of the discharge $\mathcal{Q}(\vec{\theta})$ using
enables computing accurate estimates of $\mathcal{T}(\theta_i)$ through
sampling, with a sufficiently large Monte Carlo sample size.  Shown in
Figure~\ref{fig:sense_bore}~(left) are estimates of these indices corresponding to the
uncertain parameters in the borehole function using 10$^6$ pseudo-random
samples in the input parameter space. 
%\footnote{Although $\mathcal{T}(\theta_i)$ might converge with much fewer
%samples depending upon the model, we consider a large number that typically
%ensures a converged estimate for the purpose of illustration.} 
These estimates are used to verify fidelity of
parameter screening based on the methodology presented in Section~\ref{sec:method}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/sense_borehole}
  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_borehole}
\caption{
Left: Sobol' total sensitivity index for uncertain parameters in the borehole
function. Right: 
estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$) is plotted
against number of samples considered for evaluating $\mu_i$. Corresponding estimates
for the converged Sobol' total effect index ($\mathcal{T}(\theta_i)$) in each case is also included in the
legend. \alennote{Can we have larger fontsizes for the right image? Also the y-axis label
needs to be modified with a widehat as done in the text now.}}
\label{fig:sense_bore}
\end{center}
\end{figure}
In Figure~\ref{fig:sense_bore}~(right), we plot estimates of the screening parameter 
$\widehat{\mathcal{C}_i\mu_i}$ for a wide range of the number of 
samples used for approximating $\mu_i$ using~\eqref{eq:mu}.
Estimates for $\widehat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$ even when small number of samples (5--10) are used. 
Consequently, the relative importance of uncertain 
parameters in the borehole function is found to be consistent 
with predictions based on the Sobol' index. 
In the considered intervals for the uncertain parameters, it is clear 
that the discharge is insensitive to $T_u$ and $T_l$. 
Moreover, the sensitivity to $K_w$ is also small. We exploit these findings to reduce
the dimensionality of the problem by 
discounting the uncertainties in $T_u$, $T_l$, and $K_w$ by fixing 
them at their respective nominal values.

Our goal as discussed is to gain computational advantage by constructing
surrogates in a reduced input parameter space. To this end, we construct PCE's
in 5D and 4D spaces by fixing $\{T_u,T_l\}$ in the former and additionally
fixing $K_w$ in the latter at their respective mean values. In
Figure~\ref{fig:conv_bore}, we compare convergence of PCE's constructed in the
full space (7D) with those constructed in the two reduced spaces (4D and 5D)
using $\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}). 
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.6\textwidth]{./Figures/err_samples_borehole}
\caption{A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions. \alennote{Use different line styles
and colors. Also use thicker lines. Instead of taking log of the error, just use a 
semilogy in Matlab to use logarithmic scale on the y-axis.}}
\label{fig:conv_bore}
\end{center}
\end{figure}

As expected, it is observed that the PCE constructed in the 4D space converges
at a much faster rate. For instance, if a PCE with $\mathcal{O}(10^{-4})$
accuracy is sought, we need function evaluations at only about 50 sample points
in the 4D parameter space whereas the number of samples needed in the full 7D
space seems much higher.~\alennote{How are these samples used? Are we doing 
Latin Hypercube sample, or some other QMC approach?}

As discussed earlier in this section, the reduced order PCE's are verified for
predictive accuracy in a least-squares sense and a probabilistic sense.
Estimates for $\epsilon_{\mbox{\tiny{L-2}}}$ based on 50 samples and
corresponding function evaluations in the original 7D parameter space were
found to be 0.0551 and 0.0112 for the 4D and 5D PCE's respectively. In other
words, the 4D PCE is accurate within 5.52$\%$ and the 5D PCE is accurate within
1.12$\%$ of predictions based on the borehole function. We note  that although
the convergence in the case of a 5D PCE is slower (Figure~\ref{fig:conv_bore}),
its predictive accuracy is higher than the 4D PCE. This illustrates the
tradeoff between accuracy and computational efficiency for the present 
problem. Generally, the required level of accuracy is problem dependent. 
The present framework allows for moving towards higher fidelity 
reduced order surrogates based on the ranking of the parameter sensitivities.

%A possible explanation for this observation is that above a certain order
%of convergence, the uncertainty in $k_w$ contributes much more towards
%predictive accuracy of the reduced order PCE. It is therefore critical to
%account for the order of PCE convergence as well as its predictive accuracy for
%a given application, as highlighted earlier in section~\ref{sec:method}.

Figure~\ref{fig:pdfcomp_bore} illustrates a comparison of the PDF's of the
discharge, $\mathcal{Q}$ obtained by propagating 10$^6$ Monte-Carlo (MC)
samples through the 7D PCE in the original input parameter domain as well as
the reduced order PCE's constructed in 4 and 5 dimensions. 
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.6\textwidth]{./Figures/pdf_comp_borehole}
\caption{A comparison of PDF's of the discharge, $\mathcal{Q}$ as obtained
by propagating
parametric uncertainties through the 4D, 5D, and 7D PCE's.These PDF's 
were obtained using 10$^{6}$ MC samples in the input parameter domain.
\alennote{Use thicker lines, different colors in addition to line styles, larger 
font size, and also use the x-axis limits to be $[0, 300]$, maybe? 
Once figures 4, 5 are appropriate reformatted, I would combine them in one line as I did 
things in figure 2.}
} 
\label{fig:pdfcomp_bore}
\end{center}
\end{figure}
It is evident from this plot, that the PDF's agree quite favorably with each
other. Consequently, it can be said that the reduced order PCE is verified in a
probabilistic sense. In other words, the mode as well as the uncertainty in the
observable is reliably captured and predicted by the reduced order PCE.
